Self Regulation Ontology Retest Analyses

### 2018-10-15 code/SRO_Retest_Analyses.Rmd
refactoring

Measure level plot

```{r warning=FALSE, message=FALSE}
lit_review = lit_review %>%
  select(-reference)
```

```{r warning= FALSE, message =FALSE, echo=FALSE}

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Lit_Review_Plot.jpg')
```

Because this plot is difficult to digest we summarize it on a task level to give a general sense of the main takeaways. This plot naturally disregards much of the fine grained information.

```{r}
p1_t_legend <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) +
  geom_point(aes(size=sample_size, shape = type), color='black')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'bottom',
        axis.text.x = element_text(size=20),
        axis.title.x = element_text(size=20),
        legend.text = element_text(size=16),
        legend.key.width = unit(0.75, "inches"),
        legend.title = element_text(size=20),
        legend.spacing.x = unit(0.5, "inches"),
        legend.box = "vertical",
        legend.direction = "horizontal",
        plot.caption = element_text(family = "Times", size = 40, lineheight = 2, hjust = 0)) +
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15), name="Type")+
  scale_size_continuous(name = "Sample Size",
                        limits = c(10, 1200),
                        range = c(1, 40),
                        breaks = c(10, 100, 1000))+
  guides(#size = guide_legend(override.aes = list(breaks = c(10, 100, 1000)), labels = c(10, 100, 1000)),
         shape = guide_legend(override.aes = list(size = 16)))+
  geom_vline(xintercept = 0, color = "red", size = 1)+
  labs(caption = str_wrap("FIGURE 1: Summary of the literature review for tasks (left) and surveys (right). Each point represents a study containing test-retest reliability data on an unspecified dependent measure for a given task. The size of the point depends on the sample size of the study and the shape depends on the metric that was used to estimate reliability. Each vertical red line indicates 0 reliability.", width = 120))

p1_t <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) +
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) +
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15))+
  scale_size_continuous(range = c(1, 40),
                        limits = c(10,1200))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p2_t <- lit_review %>%
  filter(task == 'survey') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) +
  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) +
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
  scale_shape_manual(breaks = c("ICC","Pearson","Spearman"),
                     values = c(17, 16, 15))+
  scale_size_continuous(range = c(1, 40),
                        limits = c(10,1200))+
  geom_vline(xintercept = 0, color = "red", size = 1)

mylegend<-g_legend(p1_t_legend)
mycaption<-g_caption(p1_t_legend)

p3_t <- arrangeGrob(arrangeGrob(p1_t, p2_t, nrow=1), mylegend, mycaption, nrow=3, heights=c(10, 1, 1.5))

ggsave('Lit_Review_Plot_t.tiff', plot = p3_t, device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 52, units = "in", limitsize = FALSE, dpi = 250)
```

```{r}
rm(p1_t, p2_t, p3_t, mylegend, p1_t_legend)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Lit_Review_Plot_t.jpg')
```

An interactive version of this plot could be find [here](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/Lit_Review_Figure.html)

@@

Are there differences between clinical and non-clinical samples in the literature?

```{r}
tmp = lit_review %>%
  mutate(clinical = as.character(clinical),
         clinical = ifelse(clinical == "", "control", clinical),
         clinical_1_0 = ifelse(clinical == "control", 0, 1))
table(tmp$clinical)
table(tmp$clinical_1_0)
summary(lmer(retest_reliability ~ clinical_1_0+(1|dv),data=tmp))
```

@@

```{r}
tmp = demog_boot_df %>%
  group_by(dv) %>%
  summarise(median_icc = quantile(icc, probs=0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975)) %>%
  arrange(-median_icc)
tmp
```

```{r}
sjt.df(tmp%>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/demog_rel_table.doc")
```

@@

for(i in 1:length(names(test_demog))){
  if(is.numeric(test_demog[,i])){
    numeric_cols <- c(numeric_cols, names(test_demog)[i])
  }
}

demog_rel_df <- data.frame(icc = rep(NA, length(numeric_cols)))

row.names(demog_rel_df) <- numeric_cols

for(i in 1:length(numeric_cols)){
  demog_rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
}

demog_rel_df = demog_rel_df %>%
  mutate(var = row.names(.)) %>%
  select(var, icc) %>%
  arrange(-icc)
```

Checking low reliability demog vars: Mostly NA's

```{r}
test_demog$HowOftenHazardousCannabis
retest_demog$HowOftenHazardousCannabis

test_demog$CaffieneOtherSourcesDayMG
retest_demog$CaffieneOtherSourcesDayMG

test_demog$SpouseParentsComplainDrugUse
retest_demog$SpouseParentsComplainDrugUse

test_demog$OtherDebtAmount
retest_demog$OtherDebtAmount
```

>>>>

```{r echo=FALSE, out.width='100%'}
fig_name = 'Lit_Review_Plot_t.jpeg'

knitr::include_graphics(paste0(fig_path, fig_name))
```

An interactive version of this plot could be find [here](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/Interactive_Figures.html)

@@

@@

```{r}
demog_boot_df %>%
  group_by(dv) %>%
  summarise(median_icc = quantile(icc, probs=0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975)) %>%
  arrange(-median_icc)
```

@@

```{r}
demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc'))

demog_rel_df %>%
  select(dv, icc) %>%
  arrange(-icc)
```
